\newcommand{\inlcontent}{
	\cvitem{Idaho National Laboratory (INL), Idaho Falls, ID}
				{Senior Computational Scientist, Scientific Computing and Artificial Intelligence Division, \newline Computational Frameworks Department}
				{August 2025--present}
	[
		\item Managing over \$5.5M worth of projects and grants focused on fusion energy modeling and simulation, \\ 
					data ecosystems, digital engineering, and magnet technology.
		\item Leading fusion energy modeling and simulation strategic coordination and stakeholder engagement at INL \\
					related to the United States Department of Energy (U.S. DOE) Genesis Mission.
		\item Developing high performance computing and data ecosystem infrastructure for the INL Fusion Safety \\
					Program Archive.
		\item Leading code validation and benchmarking efforts for the Blanket Collaborative on Test Facilities \\
					(a U.S. DOE-funded Fusion Innovation Research Engine, or FIRE, Collaborative).
		\item Co-leading development of the Software for Advanced Large-scale Analysis of MAgnetic confinement \\
					for Numerical Design, Engineering \& Research (\href{https://salamander.inl.gov}{SALAMANDER}) and Tritium Migration Analysis \\
					Program, version 8 (\href{https://tmap8.inl.gov}{TMAP8}) codes for fusion digital twins.
		\item Reviewing fusion energy proposals as a committee member within INL's Laboratory Directed Research \& \\ 
					Development (LDRD) internal funding program.
		\item Leading MOOSE Software Quality Assurance (SQA) program (audited to the ASME Nuclear Quality \\ 
					Assurance, Level 1 (NQA-1) standard).
	]
	\cvitemsub{Computational Scientist, Scientific Computing and Artificial Intelligence Division, \newline Computational Frameworks Department}
				{May 2023--August 2025}
	[
		\item Developed C++ code and Python-based documentation infrastructure for the Multiphysics Object \\ 
					Oriented Simulation Environment (MOOSE) framework.
		\item Maintained documentation infrastructure for MOOSE SQA compliance.
		\item Lead MOOSE MacOS platform build system development and co-maintainer of conda-based MOOSE \\ 
					dependency packages.
		\item Served as a subject matter expert within the division on computational electromagnetics and \\
					plasma physics.
	]
	\cvitemsub{Graduate Fellow, Scientific Computing and Artificial Intelligence Division, \newline Computational Frameworks Department}
				{Jan 2018--May 2023}
		[
		\item Created and developed the \href{https://mooseframework.inl.gov/modules/electromagnetics}{MOOSE electromagnetics physics module} as well as the INL \\ 
					advanced manufacturing code \href{https://malamute.inl.gov}{MALAMUTE}.
		\item Developed models for electromagnetic coupling to the plasma physics code \href{https://shannon-lab.github.io/zapdos}{Zapdos} as well as \\
					electric-field assisted sintering within MALAMUTE.
		]
}

\newcommand{\ornlcontent}{
	\cvitem{Oak Ridge National Laboratory (ORNL), Oak Ridge, TN}
					{Graduate Student Intern, Fusion and Materials for Nuclear Systems Division}
					{Jul 2016--Dec 2017}
	[
		\item Developed code for simple radio-frequency (RF) electromagnetic simulation in support \\ 
					of ion cyclotron resonance heating (ICRH) studies for fusion energy systems
	]
}

\newcommand{\ncsucontent}{
	\cvitem{North Carolina State University (NCSU), Nuclear Engr. Dept., Raleigh, NC}
			{Graduate Research Assistant, 4th State Applications Research Group}{Jul 2013--Jun 2016}
		[
		\item Utilized particle-in-cell codes (VSim, XPDP1) to study capacitively-coupled RF \\ 
					plasma discharges
		]
		\cvitemsub{Dean's Doctoral Fellow, NCSU College of Engineering}{Aug 2012--Jun 2013}
		[
			\item Modeled proof-of-concept Z-pinch plasma neutron source for reinforced concrete \\ 
						structural interrogation using MATLAB
		]
}
